draft

### 2021-02-25 code/BW_graph_20200203.Rmd
updated draft.Rmd with a little more

## library
```{r }
library(tidyverse)
library(readxl)
library(agricolae)
library(Hmisc)
library(conflicted)
library(nlme)
library(effects)
conflict_scout()
conflict_prefer("filter", "dplyr")
conflict_prefer("summarize", "dplyr")
```

>>>>

## library
```{r }
library(tidyverse)
library(readxl)
library(agricolae)
library(Hmisc)
library(conflicted)
library(nlme)
library(effects)
# conflict_scout()
# conflict_prefer("filter", "dplyr")
# conflict_prefer("summarize", "dplyr")
```

### 2021-02-25 code/draft.Rmd
updated draft.Rmd with a little more

## Preparation
1. Setup
```{r setup, message=FALSE, warning=FALSE}
# Loading library here
library(conflicted)
library(knitr)
library(tidyverse)
library(extrafont)
library(readxl)
library(ggrepel)
library(ggpubr)

conflict_prefer("filter", "dplyr")
conflict_prefer("lag", "dplyr")

@@

# set path
opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
setwd(rprojroot::find_rstudio_root_file())
## path to data record on dropbox
path_rec <- "~/Dropbox/MGDB-Shared/CSR 2019 SW/ExperimentRecords/"
list.files(path_rec)

@@

## Body weight
### Overall, plotting all data
```{r}
BW <- read_excel(paste0(path_rec, "MasterMetadata-CS-SW-Oct2019-20200701-JW.xlsx"), sheet = "BodyWeightRecords") %>% filter(!is.na(Weight_g))
BW$BirthMode = factor(BW$BirthMode, levels = c("VF", "CSR", "CS"))

@@

BW_sum <- BW %>% group_by(TimePoint_Days, BirthMode, Sex) %>% summarise(N = n(), Mean = mean(Weight_g), SE = sd(Weight_g)/sqrt(N-1))

y_max <- ceiling(max(BW$Weight_g)/4)*4
ggplot(BW, aes(x = TimePoint_Days, y = Weight_g, color = BirthMode)) +
    geom_point(size = 0.5, alpha = 0.5) +
    geom_path(aes(group = MouseNo), color = "grey", size = 0.5, alpha = 0.5) +
    geom_smooth(aes(fill = BirthMode), alpha = 0.3) +
    geom_text_repel(data = BW_sum, aes(x = TimePoint_Days, y = Mean, label = N), size = 4, show.legend = F) +
    facet_grid(.~Sex) +
    scale_x_continuous(breaks = c(seq(7, current_days, 7)), labels = c(seq(7, current_days, 7))/7) + 
    scale_y_continuous(breaks = seq(2, y_max, 4)) +
    scale_color_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
    scale_fill_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
    labs(x = "Sampling_Week", y = "Body Weight(g)", title = "C-Section Restoration Project - Body Weight Plots-AllData") +
    theme_Publication() + theme(panel.grid.minor = element_blank())
```

@@

BW_dat <- BW %>% filter(TimePoint_Weeks<=date_range[2], TimePoint_Weeks>=date_range[1])

@@

ggplot(BW_dat, aes(x = TimePoint_Weeks, y = Weight_g, color = BirthMode)) +
    geom_point(data = BW, size = 0.5, alpha = 0.5) +
    geom_path(data = BW, aes(group = MouseNo), color = "grey", size = 0.5, alpha = 0.5) +
    stat_summary(data = BW %>% filter(TimePoint_Weeks>=10), geom = "point", fun = "mean", size = 1) +
    stat_summary(data = BW %>% filter(TimePoint_Weeks>=10), geom = "line", fun = "mean", linetype = "dashed") +
    geom_ribbon(data = BW_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean, ymin = Lwr, ymax = Uwr, fill = BirthMode), alpha = 0.3) +
    geom_point(data = BW_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean), size = 1.5) +
    geom_line(data = BW_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean)) +
    geom_label_repel(data = BW_dat_test_sum2, aes(label = groups), size = 6/.pt, label.padding = 0.1) +
    facet_grid(.~Sex) +
    scale_x_continuous(breaks = c(seq(2, 18, 1))) + 
    scale_color_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
    scale_fill_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
    labs(x = "Sampling_Week", y = "Body Weight(g)", title = "C-Section Restoration Project - Body Weight", subtitle = str_wrap("Mean and 95% CI were plotted between week 2 and 10; ANOVA test with duncan's multiple range tests were performed at each week between week 2 and 10. After week 10, only mean of each group was plotted due to very low sample size", width = 120)) +
    theme_Publication() + theme(panel.grid.minor = element_blank(), aspect.ratio = 0.8, plot.title = element_text(hjust = 0))
set_panel_size(file = "results/figs/exploratory/BW.pdf", width = unit(4, "in"), height = unit(3.2, "in"), useDingbats = F)
```

## Body Weight gain relative to week 2
```{r}
BW <- read_excel(paste0(path_rec, "MasterMetadata-CS-SW-Oct2019-20200701-JW.xlsx"), sheet = "BodyWeightRecords") %>% filter(!is.na(Weight_g))
BW$BirthMode = factor(BW$BirthMode, levels = c("VF", "CSR", "CS"))

BW_f <- BW %>% filter(ExperimentSet=="Set1-BW", TimePoint_Weeks!=1) %>% arrange(TimePoint_Weeks) %>% group_by(MouseID) %>% mutate(Weight_gain = Weight_g - Weight_g[1])

date_range <- c(2, 10)

@@

BW_f_dat_stat_sum <- BW_f_dat %>% group_by(TimePoint_Weeks, BirthMode, Sex) %>% summarise(Mean_cl = Hmisc::smean.cl.normal(x = Weight_gain) %>% paste(collapse = "-"), N = n())

%>% separate(Mean_cl, into = c("Mean", "Lwr", "Uwr"), sep = "-", convert = T) %>% ungroup

ggplot(BW_dat, aes(x = TimePoint_Weeks, y = Weight_g, color = BirthMode)) +
    geom_point(data = BW, size = 0.5, alpha = 0.5) +
    geom_path(data = BW, aes(group = MouseNo), color = "grey", size = 0.5, alpha = 0.5) +
    stat_summary(data = BW %>% filter(TimePoint_Weeks>=10), geom = "point", fun = "mean", size = 1) +
    stat_summary(data = BW %>% filter(TimePoint_Weeks>=10), geom = "line", fun = "mean", linetype = "dashed") +
    geom_ribbon(data = BW_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean, ymin = Lwr, ymax = Uwr, fill = BirthMode), alpha = 0.3) +
    geom_point(data = BW_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean), size = 1.5) +
    geom_line(data = BW_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean)) +
    geom_label_repel(data = BW_dat_test_sum2, aes(label = groups), size = 6/.pt, label.padding = 0.1) +
    facet_grid(.~Sex) +
    scale_x_continuous(breaks = c(seq(2, 18, 1))) + 
    scale_color_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
    scale_fill_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
    labs(x = "Sampling_Week", y = "Body Weight(g)", title = "C-Section Restoration Project - Body Weight", subtitle = str_wrap("Mean and 95% CI were plotted between week 2 and 10; ANOVA test with duncan's multiple range tests were performed at each week between week 2 and 10. After week 10, only mean of each group was plotted due to very low sample size", width = 120)) +
    theme_Publication() + theme(panel.grid.minor = element_blank(), aspect.ratio = 0.8, plot.title = element_text(hjust = 0))

>>>>

## Preparation
1. Setup
```{r setup, message=FALSE, warning=FALSE}
# Loading library here
library(knitr)
library(tidyverse)
library(readxl)
library(ggrepel)
# library(ggpubr)

@@

# set path
opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
setwd(rprojroot::find_rstudio_root_file())
## path to data record on dropbox
path_rec <- "~/Dropbox/IFNH CSR/ExperimentRecords/"
list.files(path_rec)

@@

## Body weight
### Overall, plotting all data
```{r}
BW <- read_excel(paste0(path_rec, "MasterMetadata-CS-SW-Oct2019-20210224-HS.xlsx"), sheet = "BodyWeightRecords", range = "A1:T2009") %>% filter(!is.na(Weight_g))
BW$BirthMode = factor(BW$BirthMode, levels = c("VF", "CSR", "CS"))

@@

BW_sum <- BW %>% group_by(TimePoint_Days, BirthMode, Sex) %>% summarise(N = n(), Mean = mean(Weight_g), SE = sd(Weight_g)/sqrt(N))

y_max <- ceiling(max(BW$Weight_g)/4)*4
ggplot(BW, aes(x = TimePoint_Days, y = Weight_g, color = BirthMode)) +
    geom_point(size = 0.5, alpha = 0.5) +
    geom_path(aes(group = MouseNo), color = "grey", size = 0.5, alpha = 0.5) +
    geom_smooth(aes(fill = BirthMode), alpha = 0.3) +
    geom_text_repel(data = BW_sum, aes(x = TimePoint_Days, y = Mean, label = N), size = 4, show.legend = F) +
    facet_grid(.~Sex) +
    scale_x_continuous(breaks = c(seq(7, current_days, 7)), labels = c(seq(7, current_days, 7))/7) + 
    scale_y_continuous(breaks = seq(2, y_max, 4)) +
    scale_color_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
    scale_fill_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
    labs(x = "Sampling_Week", y = "Body Weight(g)", title = "C-Section Restoration Project - Body Weight Plots-AllData") +
    theme_jw() + theme(panel.grid.minor = element_blank())
```

@@

BW_dat <- BW %>% dplyr::filter(TimePoint_Weeks<=date_range[2], TimePoint_Weeks>=date_range[1])

@@

ggplot(BW_dat, aes(x = TimePoint_Weeks, y = Weight_g, color = BirthMode)) +
    geom_point(data = BW, size = 0.5, alpha = 0.5) +
    geom_path(data = BW, aes(group = MouseNo), color = "grey", size = 0.5, alpha = 0.5) +
    stat_summary(data = BW %>% filter(TimePoint_Weeks>=10), geom = "point", fun = "mean", size = 1) +
    stat_summary(data = BW %>% filter(TimePoint_Weeks>=10), geom = "line", fun = "mean", linetype = "dashed") +
    geom_ribbon(data = BW_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean, ymin = Lwr, ymax = Uwr, fill = BirthMode), alpha = 0.3) +
    geom_point(data = BW_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean), size = 1.5) +
    geom_line(data = BW_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean)) +
    geom_label_repel(data = BW_dat_test_sum2, aes(label = groups), size = 6/.pt, label.padding = 0.1) +
    facet_grid(.~Sex) +
    scale_x_continuous(breaks = c(seq(2, 18, 1))) + 
    scale_color_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
    scale_fill_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
    labs(x = "Sampling_Week", y = "Body Weight(g)", title = "C-Section Restoration Project - Body Weight", subtitle = str_wrap("Mean and 95% CI were plotted; ANOVA test with duncan's multiple range tests were performed at each week ", width = 120)) +
    theme_jw() + theme(panel.grid.minor = element_blank(), aspect.ratio = 0.8, plot.title = element_text(hjust = 0))
set_panel_size(file = "results/figs/exploratory/BW.pdf", width = unit(4, "in"), height = unit(3.2, "in"), useDingbats = F)
```

## Body Weight gain relative to week 3
```{r}
BW_f <- BW %>% filter(ExperimentSet=="Set1-BW", TimePoint_Weeks>=3) %>% arrange(TimePoint_Weeks) %>% group_by(MouseID) %>% mutate(Weight_gain = Weight_g - Weight_g[1])

date_range <- c(4, 16)

@@

BW_f_dat %>% group_by(TimePoint_Weeks, BirthMode, Sex) %>% summarise(N = n()) %>% pivot_wider(names_from = c(BirthMode, Sex), values_from = N)

BW_f_dat_stat_sum <- BW_f_dat %>% group_by(TimePoint_Weeks, BirthMode, Sex) %>% summarise(Mean_cl = Hmisc::smean.cl.normal(x = Weight_gain) %>% paste(collapse = "-"), N = n()) %>% separate(Mean_cl, into = c("Mean", "Lwr", "Uwr"), sep = "-", convert = T) %>% ungroup

BW_f_dat_test <- BW_f_dat %>% group_by(TimePoint_Weeks, Sex) %>% t_test(Weight_gain ~ BirthMode, p.adjust.method = "none") %>% ungroup() %>% mutate(p.adj = p.adjust(p, method = "fdr"))

BW_f_dat_test_tbl1 <- BW_f_dat_test %>% pivot_wider(id_cols = c(Sex, group1, group2), names_from = TimePoint_Weeks, values_from = p.adj)

BW_f_dat_test_sum <- split(BW_f_dat, f = list(BW_f_dat$TimePoint_Weeks, BW_f_dat$Sex)) %>% lapply(., function(x){(aov(Weight_gain ~ BirthMode, data = x) %>% agricolae::duncan.test(trt = "BirthMode", console = T))$groups %>% rownames_to_column(var = "BirthMode")})

BW_f_dat_test_sum2 <- lapply(seq_along(BW_f_dat_test_sum), function(x){BW_f_dat_test_sum[[x]] %>% mutate(Weeks_sex = names(BW_f_dat_test_sum)[[x]]) %>% separate(Weeks_sex, into = c("TimePoint_Weeks", "Sex"), sep = "\\.")}) %>% do.call("rbind",.) %>% mutate(TimePoint_Weeks = as.numeric(TimePoint_Weeks))

ggplot(BW_f_dat, aes(x = TimePoint_Weeks, y = Weight_gain, color = BirthMode)) +
    geom_point(size = 0.5, alpha = 0.5) +
    geom_path(aes(group = MouseNo), color = "grey", size = 0.5, alpha = 0.5) +
    stat_summary(geom = "point", fun = "mean", size = 1) +
    stat_summary(geom = "line", fun = "mean", linetype = "dashed") +
    geom_ribbon(data = BW_f_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean, ymin = Lwr, ymax = Uwr, fill = BirthMode), alpha = 0.2, color = NA) +
    geom_point(data = BW_f_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean), size = 1.5) +
    geom_line(data = BW_f_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean)) +
    geom_label_repel(data = BW_f_dat_test_sum2, aes(label = groups), size = 6/.pt, label.padding = 0.1) +
    facet_grid(.~Sex) +
    scale_x_continuous(breaks = c(seq(2, 18, 1))) + 
    scale_color_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
    scale_fill_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
    labs(x = "Sampling_Week", y = "Body Weight(g)", title = "C-Section Restoration Project - Body Weight", subtitle = str_wrap("Mean and 95% CI were plotted starting from week 4; ANOVA test with duncan's multiple range tests were performed at each week between week 4 and 15.", width = 120)) +
    theme_jw() + theme(panel.grid.minor = element_blank(), aspect.ratio = 0.8, plot.title = element_text(hjust = 0))
